### 2013-06-24 trunk/network-science/paper.tex

	\small Institute for Interdisciplinary Information Sciences,
	Tsinghua University \\[2em]
	\normalsize
	June 24, 2013\\[3em]
\end{center} \par %>>>

@@

\subsection{Dynamic Metrics}
Networks contain too much information to be easily observed by people without
any abstraction. To study a network, people exploited the basic form of
quantification to concentrate on specific features of the whole graph, or an
individual vertex. Our work is to promote this method to the dynamic graphs. We
basically design new dynamic metrics according to existing successful static
ones, but we will point out a important metric that can be only observed in
time evolving networks, the activity. Intuitively speaking, a vertex with high
activity indicates more frequent recent social actions, and the vertex is more
willing to make new change by the structural sense of graph.  The accuracy of
activity will be quite vital to recommendation algorithms of advertisement, new
friends, or search results. Activity can be also used by other metrics, so that
the computation of other metrics will no longer need the time information
directly, but referring to the activity instead.

Centrality, usually defined on vertices, is frequently used to measure the
importance of a specific node in graphs of all kinds. There are many previous
studies about the static graph centralities\cite{newman2010networks}, such as
PageRank algorithm\cite{page1999pagerank}, and there are many useful network
analysis algorithms that used some kind of graph centralities. However, most
social networks change over time, and even more unfortunately, some of the
networks are large-scaled, which could make the analysis become hard and
costly, hence limit the scale of meaningful data mining. Moreover, the time
effect can also become a factor of the centrality, that is, the same graph with
different evolving sequence may have totally different metrics. On an intuitive
level, the node connected with more higher activity nodes should be more
important at that time, even if other node have much more silent neighbors. If
we do not excavate the information on the time dimension, we will lose
tremendous information and also the possibility of accumulative computation
which could be helpful in enhancement the speed of answering consistent
querying.

>>>>

	\small Institute for Interdisciplinary Information Sciences,
	Tsinghua University \\[2em]
	\normalsize
\end{center} \par %>>>

@@

\subsection{Dynamic Metrics}
Networks contain too much information to be easily observed by people without
any abstraction. To study a network, people exploited the basic form of
quantification to concentrate on specific features of the whole graph, or an
individual vertex. Our work is to promote this method to the dynamic graphs. We
basically design new dynamic metrics according to existing successful static
ones, but we will point out a important metric that can be only observed in
time evolving networks, the activity. Intuitively speaking, a vertex with high
activity indicates more frequent recent social actions, and the vertex is more
willing to make new change by the structural sense of graph.  The accuracy of
activity will be quite vital to recommendation algorithms of advertisement, new
friends, or search results. Activity can be also used by other metrics, so that
the computation of other metrics will no longer need the time information
directly, but refer to the activity instead.

Centrality, usually defined on vertices, is frequently used to measure the
importance of a specific node in graphs of all kinds. There are many previous
studies about the static graph centralities\cite{newman2010networks}, such as
PageRank algorithm\cite{page1999pagerank}, and there are many useful network
analysis algorithms that used some kind of graph centralities. However, most
social networks change over time, and even more unfortunately, many of the
networks are large-scaled, which could make the analysis become hard and
costly, hence limit the scale of meaningful data mining. Moreover, the time
effect can also become a factor of the centrality, that is, the same graph with
different evolving sequence may have totally different metrics. On an intuitive
level, the node connected with more higher activity nodes should be more
important at that time, even if other node have much more silent neighbors. If
we do not excavate the information on the time dimension, we will lose
tremendous information and also the possibility of accumulative computation
which could be helpful in enhancement the speed of answering consistent
querying.
